---
title: "Greece_Final_Viz"
author: "Abhinav Ganesh"
date: "2022-12-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# import packages
library(dplyr)
library(tidyverse)
library(stringr)
library(ggplot2)
```

```{r}
full_sent_df <- read.csv("/Users/abhi/Desktop/Mythology/full_sent_df.csv")
```
High Polarity Magnitude means High Subjectivity, but Subjectivity varies greatly with Low Polarity Magnitude.
```{r}
full_sent_df %>%
  ggplot(aes(x=abs(polarity), y=subjectivity)) +
  geom_point()
```
Plot bar for Various Translations of the Odyssey.
It may be worth standardizing in the future if we seek to compare the relative ranking of characters in a novel across novels.
```{r}
# first calculate the overall mean polarity and subjectivity
mean_polarity <- mean(full_sent_df$polarity)
mean_subjectivity <-mean(full_sent_df$subjectivity)
  

# plot polarity
full_sent_df %>%
  filter(odysseus == "True") %>%
  ggplot(aes(x=Translation, y=polarity, fill=Translation)) +
  # plot mean bars
  geom_bar(stat="summary", fun="mean") +
  # add standard error bars
  geom_errorbar(stat="summary") + 
  geom_hline(yintercept = mean_polarity, linetype="dashed", color="red") +
  labs(title="Polarity Scores by Translation of the Odyssey", y= "Polarity Score")

# plot subjectivity
full_sent_df %>%
  filter(odysseus == "True") %>%
  ggplot(aes(x=Translation, y=subjectivity, fill=Translation)) +
  # plot mean bars
  geom_bar(stat="summary", fun="mean") +
  # add standard error bars
  geom_errorbar(stat="summary") + 
  geom_hline(yintercept = mean_subjectivity, linetype="dashed", color="red") +
  labs(title="Subjectivity Scores by Translation of the Odyssey", y= "Subjectivity Score")
```
```{r}
# plot subjectivity
full_sent_df %>%
  filter(odysseus == "True") %>%
  ggplot(aes(x=polarity, fill=Translation, alpha=0.05)) +
  # plot mean bars
  geom_density()


# after standardization, all means are 0
# plot subjectivity
full_sent_df %>%
  filter(odysseus == "True") %>%
  ggplot(aes(x=standardized_polarity, fill=Translation, alpha=0.05)) +
  # plot mean bars
  geom_density()
```


```{r}
characters_df <- read.csv("/Users/abhi/Desktop/Mythology/characters_df.csv")
```

```{r}
characters_df %>%
  filter(Translation == "Butler") %>%
  select(word, std_standardized_subjectivity)
```
Plotting the mean of the standardized polarities across all translations for each character.
We can see that antagonists (antinous, circe, polyphemus, poseidon, scylla) all have negative means. Calypso has a positive mean but perhaps this is because she is described with positive words (e.g. beautiful, etc.). 
Monsters (circe, polyphemus, poseidon, scylla) have overall negative polarity because they are often antagonists.
```{r}
# translation_of_interest = "All"
# characters_df %>%
#   filter(Translation == translation_of_interest) %>%
#   ggplot(aes(x=word, y=mean_standardized_polarity, fill=word)) +
#   # plot mean bars
#   geom_bar(stat="summary", fun="identity") +
#   # add standard error bars
#   # geom_errorbar(mapping=aes(x=word, ymin=mean_standardized_polarity - std_standardized_polarity, ymax=mean_standardized_polarity + std_standardized_polarity)) +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
#   labs(title = paste("Mean Standardized Polarity Scores for",translation_of_interest,"Translation(s) of the Odyssey"))


translation_cats = unique(characters_df$Translation)
for (translation_of_interest in translation_cats) {
  characters_df %>%
  filter(Translation == translation_of_interest) %>%
    ggplot(aes(x=word, y=mean_standardized_polarity, fill=word)) +
    # plot mean bars
    geom_bar(stat="summary", fun="identity") +
    # add standard error bars
    #geom_errorbar(mapping=aes(x=word, ymin=mean_standardized_polarity - std_standardized_polarity, ymax=mean_standardized_polarity + std_standardized_polarity)) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
    labs(title = paste("Mean Standardized Polarity Scores for",translation_of_interest,"Translation(s) of the Odyssey"), x="Character", y="Mean Standardized Polarity Score")     -> graph_obj
  
  print(graph_obj)
}
```
However, when we plot the same graph with error bars we see very large degrees of variation which don't imply a significant difference in terms of the mean standardized polarity scores for each character. 

```{r}
# translation_of_interest = "All"
# characters_df %>%
#   filter(Translation == translation_of_interest) %>%
#   ggplot(aes(x=word, y=mean_standardized_polarity, fill=word)) +
#   # plot mean bars
#   geom_bar(stat="summary", fun="identity") +
#   # add standard error bars
#   # geom_errorbar(mapping=aes(x=word, ymin=mean_standardized_polarity - std_standardized_polarity, ymax=mean_standardized_polarity + std_standardized_polarity)) +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
#   labs(title = paste("Mean Standardized Polarity Scores for",translation_of_interest,"Translation(s) of the Odyssey"))


translation_cats = unique(characters_df$Translation)
for (translation_of_interest in translation_cats) {
  characters_df %>%
  filter(Translation == translation_of_interest) %>%
    ggplot(aes(x=word, y=mean_polarity, fill=word)) +
    # plot mean bars
    geom_bar(stat="summary", fun="identity") +
    # add standard error bars
    geom_errorbar(mapping=aes(x=word, ymin=mean_polarity - std_polarity, ymax=mean_polarity + std_polarity)) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
    labs(title = paste("Mean Polarity Scores for",translation_of_interest,"Translation(s) of the Odyssey"), x="Character", y="Mean Polarity Score")     -> graph_obj
  
  print(graph_obj)
}
```


```{r}
# comparing the standardized means overall
characters_df %>%
  filter(Translation != "All") %>%
  ggplot(aes(x=word, y=mean_standardized_polarity)) +
  # plot mean bars
  #geom_bar(stat="summary", fun="mean") +
  geom_point(stat="summary", fun="mean", size=4, shape=21, fill="white")+
  # add standard error bars
  geom_errorbar(stat="summary") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
  labs(title = paste("
  Mean Standardized Polarity Scores of Characters 
  across all Translations of the Odyssey"), 
  x="Character", y="Mean Standardized Polarity Score")
  #geom_hline(yintercept = mean_polarity, linetype="dashed", color="red")
```
Compare between characters of different economic statuses
```{r}
# demographic_groups = c("Creature_Type", "Gender", "Economic_Status")

# comparing the standardized means overall
characters_df %>%
  filter(Translation != "All") %>%
  ggplot(aes(x=Creature_Type, y=mean_standardized_polarity)) +
  # plot mean bars
  #geom_bar(stat="summary", fun="mean") +
  geom_point(stat="summary", fun="mean", size=4, shape=21, fill="white") +
  # add standard error bars
  geom_errorbar(stat="summary") +
  labs(title = paste("
  Mean Standardized Polarity Scores of between Creature Types 
  across all Translations of the Odyssey"), 
  x="Creature Type", y="Mean Standardized Polarity Score") -> graph_obj
  #geom_hline(yintercept = mean_polarity, linetype="dashed", color="red")
print(graph_obj)


# comparing the standardized means overall
characters_df %>%
  filter(Translation != "All") %>%
  ggplot(aes(x=Gender, y=mean_standardized_polarity)) +
  # plot mean bars
  #geom_bar(stat="summary", fun="mean") +
  geom_point(stat="summary", fun="mean", size=4, shape=21, fill="white") +
  # add standard error bars
  geom_errorbar(stat="summary") +
  labs(title = paste("
  Mean Standardized Polarity Scores between Gender Groups 
  across all Translations of the Odyssey"), 
  x="Gender Group", y="Mean Standardized Polarity Score") -> graph_obj
  #geom_hline(yintercept = mean_polarity, linetype="dashed", color="red")
print(graph_obj)


# comparing the standardized means overall
characters_df %>%
  filter(Translation != "All") %>%
  ggplot(aes(x=Economic_Status, y=mean_standardized_polarity)) +
  # plot mean bars
  #geom_bar(stat="summary", fun="mean") +
  geom_point(stat="summary", fun="mean", size=4, shape=21, fill="white") +
  # add standard error bars
  geom_errorbar(stat="summary") +
  labs(title = paste("
  Mean Standardized Polarity Scores of Economic Groups 
  across all Translations of the Odyssey"), 
  x="Economic Group", y="Mean Standardized Polarity Score") -> graph_obj
  #geom_hline(yintercept = mean_polarity, linetype="dashed", color="red")
print(graph_obj)
```
How does the translator impact the framing of a character?
We see interesting variations w the following
```{r}
characters_of_interest = list("Polyphemus", "Scylla", "Euryclea", "Calypso", "Antinous", "poseidon", "zeus")

for (charac in characters_of_interest) {
  characters_df %>%
    filter(Translation != "All") %>%
    filter(word == tolower(charac)) %>%
    ggplot(aes(x=Translation, y=mean_standardized_polarity, fill=Translation)) +
    # plot mean bars
    geom_point(stat="summary", fun="mean", size=4, shape=21) +
    #geom_bar(stat="summary", fun="identity") +
    # add standard error bars
    # SE  = SD/sqrt(n)
    geom_errorbar(mapping=aes(x=Translation, ymin=mean_standardized_polarity - std_standardized_polarity/sqrt(n), ymax=mean_standardized_polarity + std_standardized_polarity/sqrt(n))) +
    labs(title = paste("Mean Standardized Polarity Scores for",charac,"
                       across Translation(s) of the Odyssey"), x="Translation", y="Mean Standardized Polarity Score")     -> graph_obj
  
  print(graph_obj)
}
```

```{r }
characters_df %>%
    filter(Translation != "All") %>%
    ggplot(aes(x=Translation, y=mean_standardized_polarity, fill=Translation)) +
    # plot mean bars
    #geom_point(stat="summary", fun="mean", size=4, shape=21) +
    #geom_bar(stat="summary", fun="identity", position = position_dodge()) +
    # add standard error bars
    geom_errorbar(mapping=aes(x=Translation, ymin=mean_standardized_polarity - std_standardized_polarity/sqrt(n), ymax=mean_standardized_polarity + std_standardized_polarity/sqrt(n))) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    facet_wrap(~ word, nrow=2) +
    labs(title = paste("Standard Error of Mean Standardized Polarity Scores for Characters
                       across Translation(s) of the Odyssey"), x="Translation", y="Polarity Score")
```

